Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-16 Documentation/manuscript.tex
h

\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%

@@

\journalname{Sankhya B}

\begin{document}

@@

<<echo = FALSE>>=
# Creating dataframe to visualize - one subject's questions for 5 days
split.form <- function(set, nrem = 2, bound = 0){

set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
    ind <- sample(1:8, nrem)
    x[ind] <- NA
    as.numeric(x)
  }))

  return(set)

}
@

<<echo = FALSE>>=
wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
  id <- sample(2:45, size=nmiss)
  for (i in 1:nmiss) {
    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
  }
  return(set)
}
@

<<warning=FALSE, echo = FALSE>>=
cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
fill <- matrix(1, 45, 8)
dat <- data.frame(fill)
colnames(dat) <- cols
dat$Day <- seq.int(nrow(dat))
set.seed(1234)
split.dat <- split.form(dat)[1:8]
#split.dat
@

<<warning=FALSE,message=FALSE,echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- split.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
@

<<warning=FALSE,echo=FALSE>>=
cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
fill <- matrix(1, 45, 8)
dat <- data.frame(fill)
colnames(dat) <- cols
dat$Day <- seq.int(nrow(dat))
set.seed(1234)
alternate.split.dat <- split.form(dat, bound = 3)[1:8]
#alternate.split.dat
@

<<warning=FALSE,message=FALSE,echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
@

<<echo=FALSE>>=
set.seed(1234)
wave.dat <- wave.des(dat,11)
#wave.dat
@

<<echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- wave.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

<<>>=
load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)

@

>>>>

\documentclass{svjour3}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%

@@

\journalname{Sankhya B}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
\end{figure}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData"}\hlstd{)}
\hlstd{high} \hlkwb{<-} \hlstd{d}

\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData"}\hlstd{)}
\hlstd{med} \hlkwb{<-} \hlstd{d}

\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData"}\hlstd{)}
\hlstd{low} \hlkwb{<-} \hlstd{d}

\hlkwd{library}\hlstd{(xtable)}
\hlkwd{print}\hlstd{(}\hlkwd{xtable}\hlstd{(}\hlkwd{cbind}\hlstd{(}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlkwd{rbind}\hlstd{(low[[}\hlnum{1}\hlstd{]],med[[}\hlnum{1}\hlstd{]],high[[}\hlnum{1}\hlstd{]],low[[}\hlnum{2}\hlstd{]],med[[}\hlnum{2}\hlstd{]],high[[}\hlnum{2}\hlstd{]],low[[}\hlnum{3}\hlstd{]],med[[}\hlnum{3}\hlstd{]],high[[}\hlnum{3}\hlstd{]])),}\hlkwc{digits}\hlstd{=} \hlnum{3}\hlstd{),}\hlkwc{include.rownames}\hlstd{=}\hlnum{FALSE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## % latex table generated in R 3.5.0 by xtable 1.8-2 package
## % Tue May 15 15:43:01 2018
## \begin{table}[ht]
## \centering
## \begin{tabular}{lllrrrr}
##   \hline
## "" & "" & "" & Coverage & Bias & MSE & FMI \\ 
##   \hline
##  &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
##    &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
##    &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
##    &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
##    &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
##    &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
##    &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
##    &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
##    &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
##    &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
##    &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
##    &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
##    &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
##    &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
##    &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
##    &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
##    &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
##    &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
##    &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
##    &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
##    &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
##    &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
##    &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
##    &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
##    &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
##    &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
##    &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
##    &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
##    &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
##    &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
##    &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
##    \hline
## \end{tabular}
## \end{table}
\end{verbatim}
\begin{alltt}
\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file '/Users/gregorymatthews/Dropbox/designedMissingnessGit/Results/tables20180509\_60\_1\_high\_hightime1.RData', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}\begin{alltt}
\hlstd{high} \hlkwb{<-} \hlstd{d}

\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData"}\hlstd{)}
\hlstd{med} \hlkwb{<-} \hlstd{d}

\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData"}\hlstd{)}
\hlstd{low} \hlkwb{<-} \hlstd{d}

\hlkwd{library}\hlstd{(xtable)}
\hlkwd{print}\hlstd{(}\hlkwd{xtable}\hlstd{(}\hlkwd{cbind}\hlstd{(}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlkwd{rbind}\hlstd{(low[[}\hlnum{1}\hlstd{]],med[[}\hlnum{1}\hlstd{]],high[[}\hlnum{1}\hlstd{]],low[[}\hlnum{2}\hlstd{]],med[[}\hlnum{2}\hlstd{]],high[[}\hlnum{2}\hlstd{]],low[[}\hlnum{3}\hlstd{]],med[[}\hlnum{3}\hlstd{]],high[[}\hlnum{3}\hlstd{]])),}\hlkwc{digits}\hlstd{=} \hlnum{3}\hlstd{),}\hlkwc{include.rownames}\hlstd{=}\hlnum{FALSE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## % latex table generated in R 3.5.0 by xtable 1.8-2 package
## % Tue May 15 15:43:01 2018
## \begin{table}[ht]
## \centering
## \begin{tabular}{lllrrrr}
##   \hline
## "" & "" & "" & Coverage & Bias & MSE & FMI \\ 
##   \hline
##  &  &  & 0.000 & 2.328 & 5.437 & 0.002 \\ 
##    &  &  & 0.969 & 0.040 & 0.514 & 0.252 \\ 
##    &  &  & 0.411 & 0.327 & 0.131 & 0.000 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.000 & 2.326 & 5.427 & 0.012 \\ 
##    &  &  & 0.989 & -0.046 & 1.196 & 0.554 \\ 
##    &  &  & 0.409 & 0.327 & 0.131 & 0.002 \\ 
##    &  &  & 0.942 & -0.000 & 0.000 & 0.007 \\ 
##    &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
##    &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
##    &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.000 & 2.328 & 5.437 & 0.002 \\ 
##    &  &  & 0.969 & 0.059 & 0.427 & 0.242 \\ 
##    &  &  & 0.409 & 0.327 & 0.131 & 0.000 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.000 & 2.326 & 5.428 & 0.010 \\ 
##    &  &  & 0.988 & 0.019 & 0.485 & 0.547 \\ 
##    &  &  & 0.413 & 0.327 & 0.131 & 0.002 \\ 
##    &  &  & 0.941 & -0.000 & 0.000 & 0.005 \\ 
##    &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
##    &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
##    &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
##    &  &  & 0.000 & 2.327 & 5.430 & 0.006 \\ 
##    &  &  & 0.980 & 0.047 & 0.289 & 0.464 \\ 
##    &  &  & 0.411 & 0.327 & 0.131 & 0.001 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 \\ 
##    &  &  & 0.000 & 2.315 & 5.375 & 0.054 \\ 
##    &  &  & 0.972 & 0.035 & 0.279 & 0.741 \\ 
##    &  &  & 0.416 & 0.328 & 0.132 & 0.007 \\ 
##    &  &  & 0.947 & -0.000 & 0.000 & 0.032 \\ 
##    &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
##    &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
##    &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
##    &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
##    \hline
## \end{tabular}
## \end{table}
\end{verbatim}
\end{kframe}
\end{knitrout}
